---
title: "Timeseries"
author: "Zahra N."
date: "2/11/2017"
output: html_document
---

```{r setup, include=FALSE}
install.packages("forecast")
library("forecast")
path <- "~/Documents/R Programming/Timeseries Analysis"
setwd(path)
getwd()
install.packages("tseries")
library("tseries")
install.packages("fBasics")
library("fBasics")
install.packages("timeDate")
library("timeDate")
install.packages("timeSeries")
library("timeSeries")


```{r}
yahoo <-read.csv("table.csv" , na.strings = "")

ya<-yahoo[,1:3]
ya
plot(ya,[,2])
plot(ya[,2],ya[,3])
ts.plot(ya[3]) ## time series plot
hist(ya[,2])
?hist
#qq plot-hit-date-mean-std-acf -pacf
seasnol plot()

?qqplot
?hit
?acfPlot
?acf
?seasonplot ## this plot belongs to the "forcast" package
## you need to arrange your data like the example of "Airpassanger" timeseries table
##seasonplot(AirPassengers, col=rainbow(12), year.labels=TRUE)


qqplot(ya[,2],ya[,3])
acf(ya)
acf(ya, "covariance")
pacf()

---------
hist(ya[,2], freq = FALSE, ylim = c(0, 0.2))
curve(dchisq(ya[,2]), col = 2, lty = 2, lwd = 2, add = TRUE) # There is problem with this code

par(mfrow=c(2,1))        # set up the graphics : number of graphes
hist(ya[,2], prob=TRUE, 12)   # histogram: relative frequency  
hist(ya[,2], prob=FALSE, 12)   # histogram: based on real faravaani (frequency)
lines(density(ya[,2]))# smooth it - ?density for details 
#qqnorm(ya[,2])             # normal Q-Q plot  
#qqline(ya[,2]) 

----------
#Descriptive Statistics in R 
  #
var(x=ya[,2], y=NULL) # Variance

?cov
  cov(x=ya[,2], y=ya[,3]) # Covariance
  #var(x=ya[,2], y=ya[,3]) # =covariance

